%-------------------------
% Bo Shang - Machine Learning Engineer Resume
% Template adapted from Sourabh Bajaj (MIT License)
% Source: https://github.com/sb2nov/resume
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeBullet}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Bo Shang} & \href{mailto:bshang@ccny.cuny.edu}{bshang@ccny.cuny.edu} \\
  Machine Learning Engineer \textbar{} Computer Vision \& Multimodal Perception & +1-929-520-0488 \\
  \href{https://cnpcshangbo.github.io/}{cnpcshangbo.github.io} \textbar{} \href{https://www.linkedin.com/in/bo-shang}{linkedin.com/in/bo-shang} \textbar{} \href{https://scholar.google.com/citations?user=TVIPpDMAAAAJ}{Google Scholar} & New York, NY \\
\end{tabular*}

\vspace{2pt}
\small Applied ML engineer with field-deployment depth in \textbf{computer vision, 3D point-cloud detection, and multimodal sensor fusion}. Trained and deployed CNN models on AWS for NYC infrastructure inspection and traffic monitoring. Comfortable owning the full loop from raw multi-sensor data $\rightarrow$ labeled datasets $\rightarrow$ model $\rightarrow$ cloud / edge deployment.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {City University of New York --- AI \& Mobility Research Lab}{New York, NY}
      {Postdoctoral Scholar}{Jul 2025 -- Present}
      \resumeItemListStart
        \resumeBullet{Evaluating and tuning \textbf{CNN-based 3D object detectors} on fixed-LiDAR highway data covering vehicles, motorcycles, bicycles, and vulnerable road users}
        \resumeBullet{Built \textbf{configuration-portable training/inference pipeline}: train on one site's sensor configuration, infer on another with different beam counts and frame rates}
        \resumeBullet{Multi-frame point cloud reconstruction to densify per-vehicle representations for downstream classification}
        \resumeBullet{Co-authored two MobiSPC 2025 papers on (a) LiDAR beam-count requirements for VRU detection and (b) a sensing-perspectives survey}
      \resumeItemListEnd

    \resumeSubheading
      {City University of New York --- Robotics Lab}{New York, NY}
      {Postdoctoral Researcher}{Dec 2022 -- Dec 2024}
      \resumeItemListStart
        \resumeBullet{Trained \textbf{CNNs for crack, spalling, and stain detection} on robot-collected bridge imagery; pushed models to \textbf{AWS} for scalable cloud inference}
        \resumeBullet{Built custom \textbf{WebODM-based platform} integrating automated segmentation, 3D reconstruction, interactive visualization, and crack measurement for end-user delivery}
        \resumeBullet{Contributed to contrastive-learning approach for robust defect mapping on concrete slabs using impact-echo data}
        \resumeBullet{Equal-first-author IROS 2025 paper (IEEE T-ASE 2025) on robotic inspection and analytics for structural defects}
      \resumeItemListEnd

    \resumeSubheading
      {Missouri University of Science and Technology}{Rolla, MO}
      {Postdoctoral Fellow}{Jan 2020 -- Nov 2022}
      \resumeItemListStart
        \resumeBullet{Designed image-processing algorithms for \textbf{girder detection} (OpenCV, C++) on the NVIDIA Jetson edge platform as part of bridge-inspection drone}
        \resumeBullet{Built visual-odometry data-quality evaluation for indoor flying-robot perching task; integrated VICON motion capture for GPS-denied flight stability}
      \resumeItemListEnd

    \resumeSubheading
      {Vaughn College of Aeronautics and Technology}{New York, NY}
      {Instructor / Adjunct}{2023 -- 2024}
      \resumeItemListStart
        \resumeBullet{Taught \textit{Principles of AI} (SBC 012), \textit{Principles of Research --- AI} (SBC 014A), and \textit{Robotics, Mechanics and Control} (MCE 355)}
        \resumeBullet{Instructor for Computer Engineering Summer Academy AI module (Jun--Aug 2024)}
      \resumeItemListEnd

    \resumeSubheading
      {University of California, Merced}{Merced, CA}
      {Junior Specialist \& Lecturer}{Sep 2015 -- Sep 2017}
      \resumeItemListStart
        \resumeBullet{Co-led \textbf{SmartCaveDrone} (ICUAS'17): SLAM platform for GPS-denied cave exploration; fused IMU with KinectFusion-style dense visual SLAM}
        \resumeBullet{Computer-vision aided localization on embedded Linux UAV; object detection with OpenCV / Python; DroneKit for autonomous navigation}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS / SKILLS-----------------
\section{Selected ML Projects}
  \resumeSubHeadingListStart
    \resumeItem{CNN-based 3D Detection on Highway LiDAR (2024--present)}{Evaluating and tuning 3D detectors on fixed roadside LiDAR for VRU classification (vehicles, motorcycles, bicycles, pedestrians). Configuration-portable pipeline across sensor variants.}
    \resumeItem{Bridge Defect Detection \& AWS Deployment (2022--present)}{Trained CNNs for crack/spalling/stain detection from drone imagery, deployed at scale on AWS, integrated into WebODM-based inspection platform.}
    \resumeItem{Contrastive Learning for Defect Mapping (2024)}{Contrastive learning approach for robust impact-echo defect mapping on concrete slabs, robust across acquisition conditions.}
    \resumeItem{Vision-Based Robotic Control (2015--2022)}{Drone visual servoing with fractional-order controllers on edge hardware; CNN girder detection on NVIDIA Jetson for BIRDS inspection drone.}
  \resumeSubHeadingListEnd

\section{Programming \& Tools}
  \resumeSubHeadingListStart
    \item\small{\textbf{Languages}: Python (primary), C++, MATLAB, Fortran, Swift}
    \item\small{\textbf{ML \& CV}: PyTorch, TensorFlow, CUDA, OpenCV, 2D/3D CNN object detection, contrastive learning, multimodal fusion (LiDAR + RGB + thermal + hyperspectral)}
    \item\small{\textbf{Cloud \& Edge}: AWS (S3, EC2, SageMaker), Docker, NVIDIA Jetson (Nano/TX2/Xavier), embedded Linux, WebODM}
    \item\small{\textbf{Data Pipelines}: ROS / ROS 2, MCAP, Protobuf, end-to-end ingestion from real sensors, dataset versioning and format conversion across configurations}
    \item\small{\textbf{Infrastructure}: Git/GitHub Actions, CI/CD, Linux/Ubuntu, AWS, model packaging and serving}
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {City College of New York (CUNY)}{New York, NY}
      {Ph.D. in Civil Engineering (Transportation) --- Fellowship}{Aug 2025 -- Present}
    \resumeSubheading
      {Northeastern University \& University of California, Merced}{Shenyang, China / Merced, CA}
      {Ph.D. in Pattern Recognition \& Intelligent Systems}{Aug 2013 -- Dec 2020}
    \resumeSubheading
      {Northeastern University}{Shenyang, China}
      {M.Eng. in Pattern Recognition \& Intelligent Systems; B.Eng. in Automation}{Aug 2007 -- Dec 2013}
  \resumeSubHeadingListEnd

\section{Selected Publications}
  \resumeSubHeadingListStart
    \resumeBullet{\textbf{Bo Shang} et al. \textit{Sensing Perspectives on Vulnerable Road User Monitoring for Traffic Safety: A Survey.} MobiSPC 2025.}
    \resumeBullet{\textbf{Bo Shang} et al. \textit{How Many Beams of LiDAR is Enough for Detecting Vulnerable Road Users?} MobiSPC 2025.}
    \resumeBullet{J. Feng, \textbf{B. Shang}, et al. \textit{Robotic Inspection and Data Analytics to Localize and Visualize the Structural Defects of Concrete Infrastructure.} IEEE T-ASE 2025. \textit{[Selected for IROS 2025; equal first author]}}
    \resumeBullet{E. Hoxha, J. Feng, $\ldots$, \textbf{B. Shang}, et al. \textit{Contrastive Learning for Robust Defect Mapping in Concrete Slabs using Impact Echo.} 2024.}
  \resumeSubHeadingListEnd

\section{Patents \& Awards}
  \resumeSubHeadingListStart
    \resumeBullet{\textbf{US 12,296,994} (granted May 2025) --- Unmanned vehicle having flight configuration and surface traverse configuration}
    \resumeBullet{\textbf{Best System Control} \& \textbf{Best Mission Planning} Awards --- International Aerial Robotics Competition (AUVSI), 2014 \textit{[team lead]}}
    \resumeBullet{\textbf{Meritorious Prize}, International Mathematical Contest in Modeling (USA), 2010}
  \resumeSubHeadingListEnd

\end{document}
